VFTS682: a confirmed dynamical ejection?

### 2018-05-09 VFTS682.tex
section on generic surroundings done, but error calculation is wrong

Throughout this study, we assume the same distance of $50$\,kpc to the star, and to
the 30 Doradus region as a whole, since the parallax for VFTS682
listed in the Gaia DR2 catalog is negative. %% this is what makes the
                                %% LOS velocity useless...how to improve?

@@

\subsection{Is it a runaway star?}
We first address the question of whether VFTS682 is a typical star in
its surroundings from the kinematic point of view, or whether it is a
runaway star with a significantly large peculiar velocity. The former is what should
be expected if it formed where we observe it today, in relative
isolation from other massive stars. We calculate the velocity relative
to the general population in its surroundings, shown as blue dots in
the large panel of \Figref{fig:main}, assuming a distance of
$D=50$\,kpc.

\todo{discuss numbers found, refer to figure}
likely conclusion looking at the general region: it is a ``bona
  fide'' runaway star with velocity components $\left(v_\mathrm{RA},
    v_\mathrm{DE}, v_\mathrm{rad}\right)$ =
  $\left(\todo{XX},\todo{YY},\todo{ZZ}\right)$, corresponding to $v\equiv\sqrt{v_\mathrm{RA}^2+v_\mathrm{DE}^2+v_\mathrm{rad}^2}=\todo{AA}\,\kms$.

>>>>

Throughout this study, we assume the same distance of $50$\,kpc to the star, and to
the 30 Doradus region as a whole.% , since the parallax for VFTS682
% listed in the Gaia DR2 catalog is negative. %% this is what makes the
%                                 % LOS velocity useless...how to improve?

@@

\subsection{Is it a runaway star?}

We first address the question of whether VFTS682 is a typical star
from the kinematic point of view, or whether it is a runaway star with
a significantly large peculiar velocity compared to its surrounding population. The former is what should
be expected if it formed where we observe it today, in relative
isolation from other massive stars.

Using the 437 stars selected as the ``surrounding population'' in
\Secref{sec:sample}, we find averaged proper motion components of
$\mu_\mathrm{RA} = 1.695\pm0.003\,\mathrm{mas\ yr^{-1}}$ and
$\mu_\mathrm{DE} = 0.691\pm0.003\,\mathrm{mas\ yr^{-1}}$. Subtracting these values from the
proper motions of VFTS682 (see \Tabref{tab:vfts682}), we obtain the
components of proper motion of the star relative to the surrounding region
$\mu^\mathrm{sur}_\mathrm{RA} = 0.14\pm 0.07\,\mathrm{mas\ yr^{-1}}$ and $\mu^\mathrm{sur}_\mathrm{DE} =
0.09\pm 0.08\,\mathrm{mas\ yr^{-1}}$. These can be converted in the
the components of the transverse velocity $v^\mathrm{sur}_\mathrm{RA}=35\pm17\,\kms$,
$v^\mathrm{sur}_\mathrm{DE}=22\pm19\,\kms$, assuming a distance of
50\,kpc (we do not account for the uncertainty in the distance
estimate when propagating errors). The radial velocity from
\cite{bestenlehner:11} then gives the third component along
the line of sight, allowing us to calculate the speed of the star:

\begin{equation}
  \label{eq:speed}
  v = \sqrt{\left(v^\mathrm{sur}_\mathrm{RA}\right)^2
    +\left(v^\mathrm{sur}_\mathrm{DE}\right)^2+\left(\delta v_\mathrm{rad}\right)^2} = 61 \pm 1
  \, \kms \ .
\end{equation}
This value for the peculiar 3D velocity of VFTS682 make it a ``bona
fide'' runaway star.

\todo{errors are wrong}
